Coupling PDEs on 3D-1D domains with Lagrange multipliers

### 2020-02-28 3d1d_coupled_LM.tex
fig next to eqs in intro

In this paper we will consider a 3D-1D coupled problem described by the following equations: 
\begin{subequations}
\label{eq:pde}
\begin{align}
\label{eq:pde1}
  -\Delta u + u + \lambda \delta_{\Lambda} &= f &\mbox{ in } \Omega,\\
\label{eq:pde2}
-\Delta \ud + \ud - \lambda &= g &\mbox{ on } \Lambda,\\
\label{eq:coupling}
T_\Lambda u - v  &=  h &\mbox{ on } \Lambda . 
\end{align}
\end{subequations}
Here, $u$ and $\ud$ are the unknown scalar fields,  $\lambda$ is the Lagrange multiplier,  $\Omega$ is a bounded domain in $\R^3$, whereas $\Lambda \subset \Omega$ is a 1D structure. 
The term $p\delta_{\Lambda}$ is a Dirac measure such that 
$\int_{\Omega}p(x)\delta_{\Lambda}v(x)\,\mathrm{d}x=\int_{\Lambda}p(t)v(t) \,\mathrm{d}t$
for a continuous function $v$.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{domain.pdf}
\end{center}
\caption{Geometrical setting of the problem}
\label{fig1}
\end{figure}

>>>>

In this paper we will consider a 3D-1D coupled problem described by the following equations:\\
\begin{minipage}{0.5\textwidth}
\begin{subequations}
\label{eq:pde}
\begin{align}
\label{eq:pde1}
  -\Delta u + u + \lambda \delta_{\Lambda} &= f &\mbox{ in } \Omega,\\
\label{eq:pde2}
-\Delta \ud + \ud - \lambda &= g &\mbox{ on } \Lambda,\\
\label{eq:coupling}
T_\Lambda u - v  &=  h &\mbox{ on } \Lambda . 
\end{align}
\end{subequations}
\end{minipage}
%
\begin{minipage}{0.45\textwidth}
\begin{figure}[H]
\begin{center}
\includegraphics[width=0.6\textwidth]{domain.pdf}
\end{center}
\caption{Geometrical setting of the problem}
\label{fig1}
\end{figure}
\end{minipage}\\
Here, $u$ and $\ud$ are the unknown scalar fields,  $\lambda$ is the Lagrange multiplier,  $\Omega$ is a bounded domain in $\R^3$, whereas $\Lambda \subset \Omega$ is a 1D structure. 
The term $p\delta_{\Lambda}$ is a Dirac measure such that 
$\int_{\Omega}p(x)\delta_{\Lambda}v(x)\,\mathrm{d}x=\int_{\Lambda}p(t)v(t) \,\mathrm{d}t$
for a continuous function $v$.

@@
